---
title: "Stat 850 Project Description"
author: "Stack Jayden, Grantham Michael"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(digits = 3)
```

```{r load-sas-libraries, echo = F, message = F, warning = F}

saspath <- "/usr/local/SASHome/SASFoundation/9.4/bin/sas_en" # Your SAS path goes here
sasopts <- "-ls 75"
knitr::opts_chunk$set(engine.path=list(sas=saspath, saslog=saspath, sashtml=saspath),
                      engine.opts=list(sas=sasopts, saslog=sasopts, sashtml=sasopts), 
                      comment=NA)
library(SASmarkdown)
```

## Instructions

Small change

Each member of your team should modify this document in some way and push their modifications to the repository in a separate commit. This will ensure that you have set your repository up in a way that ensures all group members are working with the same repository. 

Note that you must compile your readme (this document) for it to properly display as part of your github repository. 

Once you have received feedback on your project proposal (via Canvas) you may alter this README so that it describes your final project instead of the project proposal. 

## Data Set

We will use the Lahman data set in R.

This data set contains offensive and defensive statistics of every player dating back to the late 1800's. We will filter down and identify the variables that will be used in the player evaluation algorithm.  

We will also use two customized CSV files chosen by us from baseballsavant.com. This allows us to freely choose the variables that we think will properly represent a projection of both wins and OBP. Variables that will be considered are OBP, Wins, Hits, ERA, Average exit velocity allowed, Average fastball speed, Average offspeed pitch spin rate, and others. 




## Potential Topics to Explore Using the Data Set

With the development of Sabermetrics and advanced statistics in major league baseball. Position value has been revolutionized for each of the nine positions on the baseball field. Perhaps the most important player on the field is the pitcher. They are involved in 100% of plays in baseball and control many aspects of the game. We will explore an algorithm that projects pitcher success. 

Pitcher success, to an individual outside of sports, could be classified purely as the amount of wins one has in a season. Others know that there are a lot of different aspects of pitching that correlate to pitcher success. For our study, we will consider pitcher success based off of lack of hitter success. I.e. the lower on base percentage (OBP) the pitcher possess,the more successful he is. 

We will also consider the same variables as if we are newcomers to the sport conducting a similar experiment. Thus, we will be consider pitcher success to be the number of wins he wins in a season. 



## Group Members

List all of the project contributors here.  

Jayden Stack
Michael Grantham




