---
title: "Stat 850 Project Description"
author: "Stack Jayden, Grantham Michael"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(digits = 3)
```

```{r load-sas-libraries, echo = F, message = F, warning = F}

saspath <- "/usr/local/SASHome/SASFoundation/9.4/bin/sas_en" # Your SAS path goes here
sasopts <- "-ls 75"
knitr::opts_chunk$set(engine.path=list(sas=saspath, saslog=saspath, sashtml=saspath),
                      engine.opts=list(sas=sasopts, saslog=sasopts, sashtml=sasopts), 
                      comment=NA)
library(SASmarkdown)
```

## Instructions

Small change

Each member of your team should modify this document in some way and push their modifications to the repository in a separate commit. This will ensure that you have set your repository up in a way that ensures all group members are working with the same repository. 

Note that you must compile your readme (this document) for it to properly display as part of your github repository. 

Once you have received feedback on your project proposal (via Canvas) you may alter this README so that it describes your final project instead of the project proposal. 

## Data Set
<<<<<<< HEAD
We will use the Lahman data set in R.
=======
https://developer.sportradar.com/docs/read/baseball/MLB_v7_with_Statcast#play-by-play
The data contains play-by-play statistics for what looks like every player and every pitcher in the game. We will continue to use data specifically on Jose Abreu (for bias case). The data will give us the launch angle, projected distance, and exit velocity for every at bat of Jose's career. We'll also look at hit location, player ID and how it changes over the course of a career.
>>>>>>> 8609b5667e26a5d0888fe9e9ade5303898d358d1

This data set contains offensive and defensive statistics of every player dating back to the late 1800's. We will filter down and identify the variables that will be used in the player evaluation algorithm.  

We may also use the pitchRx package which includes the pitches of and pitch type of any game we can find. We can use this to provide visuals of the strike zone to create a picture of a pitcher's velocity and tendencies. 


## Potential Topics to Explore Using the Data Set

With the development of Sabermetrics and advanced statistics in major league baseball. Position value has been revolutionized for each of the nine positions on the baseball field. perhaps the two most important positions on the field are the pitcher and catcher. We will be exploring an algorithm that measures the player value of each starting catcher on each major league baseball team.

We will also consider the player value of pitchers in the league similarly to the catching position. For the sake of data, we will only consider the "ace"or the best pitcher of each team. 

Lastly, we will consider the interaction between pitcher and catcher. We will aim to find out which battery combination is the best in the MLB--comparing team to team. That is what pitcher and catcher combination is the best in the MLB. Then we will look to find out the best overall combination of pitcher and catcher in the MLB based on player value. 



## Group Members
Jayden Stack and Michael Grantham

