---
title: "Pitcher Success"
author: "Jayden Stack and Michael Grantham"
date: "11/21/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Baseball



## Slide with Bullets

- We originally wanted to set up a scouting report for every batter in the league, using some custom statistics derived from advanced batting statistics. We would then produce a heatmap and detailed scouting report of what sorts of pitches work on every batter, and where in the zone it worked. Gleefully, we set about finding our data.
- Our data exists, but isn't cheap. Back to the drawing board.
- Instead, we decided to see if we could predict the net number of wins a pitcher was worth based on his ERA (earned run average), OBP (Opponent On-base percentage), and whatever else could think of. We found a package called Lahman that would do the job.

## Slide with R Output

-Here, we're going to look at how we selected and in some cases created the column data we needed.
```{r regression echo=TRUE}
library(aod)
library(mgcv)
library(ggplot2)
#Here, we look at the relevant data from

#Select columns from the Pitching dataset
pitchers <- select(tibble(Pitching), playerID, yearID, teamID, IPouts, BB, SO, BAOpp, ERA, W, L)


#Create a Net Wins column
pitchers <- pitchers %>% mutate(NetWins = W-L)

#Only keep rows where there is no missing data
pitchers <- pitchers[complete.cases(pitchers),]

#Normalize data so that coefficients are meaningful
pitchers <- pitchers %>% mutate(normIPouts = (IPouts - mean(IPouts)) / sd(IPouts))
pitchers <- pitchers %>% mutate(normBB = (BB - mean(BB)) / sd(BB))
pitchers <- pitchers %>% mutate(normSO = (SO - mean(SO)) / sd(SO))
pitchers <- pitchers %>% mutate(normBAOpp = (BAOpp - mean(BAOpp)) / sd(BAOpp))
pitchers <- pitchers %>% mutate(normERA = (ERA - mean(ERA)) / sd(ERA))
```

## Building linear model

-Finally, we can build our model, as is accomplished below.

```{r lm echo=FALSE}

#Build Linear Model
mylm <- lm(NetWins ~ normIPouts + normBB + normSO + normBAOpp + normERA, data = pitchers)

#Analyze Findings
summary(mylm)
summary(mylm)$r.squared 

```

## Building a Generalized Additive Model

-That last model sucked. Let's try again with a better model.

```{r gam echo=FALSE}

#Note, these findings mean that our regression sucks. Trying a new regression.
mygam <- gam(NetWins ~ normIPouts + normBB + normSO + normBAOpp + normERA, data = pitchers)
summary(mygam)
summary(mygam)$r.squared

```

##Building a Generalized Linear Model

-That last model sucked too. Let's try another one--a generalized linear model.
```{r glm echo=FALSE}

#Note, these results also suck. Trying a new regression.
myglm <- glm(NetWins ~ normIPouts + normBB + normSO + normBAOpp + normERA, family = gaussian, data = pitchers)
summary(myglm)
summary(myglm)$r.squared
```

## Building models

-Wow, that went well. Let's see if we can figure out any kind of a model that works at all--even ones that are nonlinear and completely unintuitive to normal humans. Gleefully, that's what we did.

-Put on that infinity glove and snap your fingers

```{r interaction echo=FALSE}

#Note, all of these results still suck. Going to try an interaction model with everything

#Select columns from the Pitching dataset
pitchers <- tibble(Pitching)

#Create a Net Wins column
pitchers <- pitchers %>% mutate(NetWins = W-L)

#Only keep rows where there is no missing data
pitchers <- pitchers[complete.cases(pitchers),]



mylm <- lm(NetWins ~ IPouts*HR*BB*SO*BAOpp*ERA*IBB*WP*HBP*BK*BFP*GIDP, data = pitchers)

#Analyze Findings
#summary(mylm)
summary(mylm)$r.squared 
```

## After the MCU

-Well look at that, we snapped our fingers and explained just over half of the variation. Excellent work team!

-Clearly, this isn't going as well as it might've. Let's just see if we can explain pitcher success using advanced pitching metrics.


## Slide with Plot

```{r pressure}
plot(pressure)
```

