#The baseball world today contains numerous amounts of very specific data included in sabermetrics or statistical analysis of baseball records. This includes things such as exit velocity off a bat, pitch curve, and quality of contact. Let's take a look at what may factor in to Our idea of pitcher success.
```{r Advanced}
library(tidyverse)
#Read in data
advancedPitchers <-  read_csv("CSVs/AdvancedPitcherMetrics.csv")
advancedPitchers <- tibble(advancedPitchers)
advancedPitchers <- advancedPitchers %>% mutate(name=paste(first_name, last_name))

advancedPitchers <- advancedPitchers %>% mutate(name=paste(first_name, last_name))

advancedPitchers <- advancedPitchers[order(advancedPitchers$name),]


```


```{r Advanced Graphs}
library(ggplot2)
ggplot(data = advancedPitchers) + geom_point(aes(x = fastball_avg_speed, y = on_base_percent, color= year))

ggplot(data = advancedPitchers) + geom_point(aes(x = hard_hit_percent, y = on_base_percent, color= year))
#Definitely something here!

ggplot(data = advancedPitchers) + geom_point(aes(x = exit_velocity_avg, y = on_base_percent, color= year))
#maybe a tiny bit

ggplot(data = advancedPitchers) + geom_point(aes(x = launch_angle_avg, y = on_base_percent, color= year))

ggplot(data = advancedPitchers) + geom_point(aes(x = barrel_batted_rate, y = on_base_percent, color= year))

ggplot(data = advancedPitchers) + geom_point(aes(x = breaking_avg_spin, y = on_base_percent, color= year))

ggplot(data = advancedPitchers) + geom_point(aes(x = sweet_spot_percent, y = on_base_percent, color= year))
#eh kinda

ggplot(data = advancedPitchers) + geom_point(aes(x = year, y = on_base_percent, color= year))


```
We did find some statistics that had positive trends. Are the significant enough to be useful? Let's find out!
```{r first model}
mylm <- lm(on_base_percent ~  hard_hit_percent * sweet_spot_percent * exit_velocity_avg * year, data = advancedPitchers)

#Analyze Findings
summary(mylm)
summary(mylm)$r.squared 
```
Throw Everything on the pitching side.
```{r second}

mylm <- lm(on_base_percent ~  fastball_avg_speed * breaking_avg_speed * offspeed_avg_speed * fastball_avg_spin * breaking_avg_spin * offspeed_avg_spin, data = advancedPitchers)

#Analyze Findings
summary(mylm)
summary(mylm)$r.squared 

#These findings still don't really help us at all. Back to the drawing board.

```
Throw everything on the hitting side.
```{r Third model}
#Let's explore another model idea using advanced metrics for hitters
mylm <- lm(on_base_percent ~  exit_velocity_avg * launch_angle_avg * hard_hit_percent * sweet_spot_percent * barrel_batted_rate * solidcontact_percent,  data = advancedPitchers)

#Analyze Findings
summary(mylm)
summary(mylm)$r.squared 

#Again, not too useful at all. Consider something different.
```
Why is it so hard for us to find something that is significant? We have learned that it is defintely hard to find a small difference.This chart shows just that.

```{r Conclusion}
ggplot(advancedPitchers, aes(x=year, y=on_base_percent, group = year)) +
  geom_boxplot()


```





